### 2023-08-21 xFitter/PDF_profiling/EPPS21nlo_CT18Anlo_W184/syst/collectPlots.tex
Uploading xFitter results with the latest tables, including full FPF result FASERv2+FLArE10+AdvSND

\newcommand{\figw}{70mm}
\newcommand{\experiment}{FASERv2}
\newcommand{\unctype}{uncor}

@@

FASERv2 charm nochargediscrimination\\
\renewcommand{\dataset}{_charm_nochargediscrimination}
\includegraphics[width=\figw,trim={0mm 0mm 0mm 0mm},clip]{\experiment\dataset/\unctype_FASERv2_q2_10000_pdf_uv_ratio.pdf}
\includegraphics[width=\figw,trim={0mm 0mm 0mm 0mm},clip]{\experiment\dataset/\unctype_FASERv2_q2_10000_pdf_dv_ratio.pdf}\\
\includegraphics[width=\figw,trim={0mm 0mm 0mm 0mm},clip]{\experiment\dataset/\unctype_FASERv2_q2_10000_pdf_g_ratio.pdf}
\includegraphics[width=\figw,trim={0mm 0mm 0mm 0mm},clip]{\experiment\dataset/\unctype_FASERv2_q2_10000_pdf_Sea_ratio.pdf}
\includegraphics[width=\figw,trim={0mm 0mm 0mm 0mm},clip]{\experiment\dataset/\unctype_FASERv2_q2_10000_pdf_s_ratio.pdf}

>>>>

\newcommand{\figw}{70mm}
\newcommand{\experiment}{FASERv2}
\newcommand{\unctype}{syst}

@@

FASERv2 charm nochargediscrimination\\
\renewcommand{\dataset}{_charm_nochargediscrimination}
\includegraphics[width=\figw,trim={0mm 0mm 0mm 0mm},clip]{\experiment\dataset/\unctype_\experiment_q2_10000_pdf_uv_ratio.pdf}
\includegraphics[width=\figw,trim={0mm 0mm 0mm 0mm},clip]{\experiment\dataset/\unctype_\experiment_q2_10000_pdf_dv_ratio.pdf}\\
\includegraphics[width=\figw,trim={0mm 0mm 0mm 0mm},clip]{\experiment\dataset/\unctype_\experiment_q2_10000_pdf_g_ratio.pdf}
\includegraphics[width=\figw,trim={0mm 0mm 0mm 0mm},clip]{\experiment\dataset/\unctype_\experiment_q2_10000_pdf_Sea_ratio.pdf}
\includegraphics[width=\figw,trim={0mm 0mm 0mm 0mm},clip]{\experiment\dataset/\unctype_\experiment_q2_10000_pdf_s_ratio.pdf}

FASERv2+FLArE10+AdvSND\\
\renewcommand{\experiment}{FPF}
\includegraphics[width=\figw,trim={0mm 0mm 0mm 0mm},clip]{\experiment/\unctype_\experiment_q2_10000_pdf_uv_ratio.pdf}
\includegraphics[width=\figw,trim={0mm 0mm 0mm 0mm},clip]{\experiment/\unctype_\experiment_q2_10000_pdf_dv_ratio.pdf}\\
\includegraphics[width=\figw,trim={0mm 0mm 0mm 0mm},clip]{\experiment/\unctype_\experiment_q2_10000_pdf_g_ratio.pdf}
\includegraphics[width=\figw,trim={0mm 0mm 0mm 0mm},clip]{\experiment/\unctype_\experiment_q2_10000_pdf_Sea_ratio.pdf}
\includegraphics[width=\figw,trim={0mm 0mm 0mm 0mm},clip]{\experiment/\unctype_\experiment_q2_10000_pdf_s_ratio.pdf}
